
\subsection{The role of the countability axioms}

\begin{dfn}[]
  Let $X,Y$ be topological spaces. A map $f: X \to  Y$ is called \textbf{sequentially continuous}, if for all sequences $\left(x_{n}\right)_{n \in \N})$ converging to $a$ in $X$, the sequence of their images $\left(f(x_{n})\right)_{n \in \N}$ converges to $f(a)$.
\end{dfn}
If $f$ is continuous, it is automatically sequentially continuous, as for a neighborhood $V$ of $f(a)$, there exists a neighborhood $U$ of $x$ such that $f(U) \subseteq V$.
And because the sequence converges
there exists an $N \in \N$ such that $n \geq N \implies x_n \in U \implies f(x_n) \in V$.

On the contrary, the opposite is not always true as we will see later.

\begin{lem}[]
Let $f: X \to  Y$ be function between continuous spaces and where $X$ satisfies the 1AA. Then
$f$ continuous $\iff$ $f$ sequentially continuous.
\end{lem}
\begin{proof}
We show contraposition:
Assume that $f$ is not continuous, so there exists a point $a \in X$ and a neighborhood $V$ of $f(a)$ such that all neighborhoods $U$ of $a$ do not satisfy $f(U) \subseteq V$.

Let $\mathcal{U} = \{U_1,U_2\ldots\}$ be countable neighborhood basis of $a$.
Then $\forall n$, chose an $x_n \in U_1 \cap \ldots \cap U_n$ with $f(x_n) \notin V$.
Clearly, this sequence converges to $a$ since for any neighborhood $U$ of $a$ there exists an $N \in \N$ such that $U$ is a neighborhood of $x_n$ which contains an element of $\mathcal{U}$.
Also,$f(x_n)$ clearly does not converge since $f(a) \notin V$.
\end{proof}



\begin{ex}[]
  Let $X = \Hom_{\Top}([0,1],[0,1])$ be the space of continuous functions with the subspace topology of $\Hom_{\Set}([0,1],[0,1]) = [0,1]^{[0,1]}$ with the product topology.

  We can show in the exercise classes that 
  \begin{align*}
    \lim_{n \to \infty} \phi_n = \phi \iff \lim_{n \to \infty}\phi_n(s) = \phi(s) \forall s \in [0,1]
  \end{align*}

  If chose the same space $X$, but with the topology $\tau_d$ induced by the $L$-metric 
  \begin{align*}
    d(\phi, \psi) = \int_0^{1} \abs{\phi(s) - \psi(s)}ds
  \end{align*}
  then the map
  \begin{align*}
    f: (X,\tau_{\text{prod}}) \to (Y,\tau_{d}), \quad \phi \mapsto  \phi
  \end{align*}
  is sequentially continuous but not continuous.

  By using the majorised converges theorem (and the majorant $1$), we get
  \begin{align*}
    \lim_{n \to \infty}\phi_n(s) = \phi(s) \implies \lim_{n \to \infty} \int_0^1 \abs{\phi_n(s) - \phi(s)} ds = 0
  \end{align*}

  The map $f$ is discontinuous at for example the constant function $\phi = 0$.

  Let $0 < \epsilon < 1$ and $V = B_{\epsilon}(f(\phi_0)) \subseteq (X,\tau_{d})$.

  We now show that all neighborhoods $U \subseteq (X,\tau_{\text{prod}})$ of $\phi$, $f(U) \nsubseteq V$.

  Let $U$ be such a neighborhood of $\phi$. Then there exists $s_1, \ldots, s_m \in [0,1]$ and $U_i \subseteq [0,1]$ open with $00in U_i$ such that
  \begin{align*}
    U 
    &\supseteq \pi_{s_1}^{-1}(U_1) \cap \ldots \cap \pi_{s_m}^{-1}(U_m)\\
    &= \{\psi: [0,1] \to [0,1] \big\vert \phi_i(s_i) \in U_i, \phi \text{ continuous}\}
  \end{align*}
  but because the condition only covers finitely any $i$ we can construct a function $\psi$ which is $0$ at each $s_i$, but almost everywhere else has value $1$.

  So $\psi \in U$ but clearly
  \begin{align*}
    d(\phi,\psi) = \int_0^1 \abs{\psi(s)} ds > \epsilon
  \end{align*}
\end{ex}


\begin{dfn}[]
A topological space $X$ is called \textbf{sequentially compact} if every sequence has a converging subsequence.
\end{dfn}
Generally speaking, compactness and sequential compactness do not imply eachother.
But some implications are true

\begin{lem}[]
  If $X$ satisfies the 1AA, then
\begin{itemize}
  \item $X$ compact $\implies$ $X$ sequentially compact
  \item If $X$ is a metric space, then $X$ sequentially compact $\iff X$ compact.
\end{itemize}
\end{lem}
\begin{proof}
Let $X$ be compact.
\begin{itemize}
  \item Let $\left(x_{n}\right)_{n \in \N}$ be a sequence in $X$.
    We want to find an $a \in X$ such that for all neighborhoods $U$ of $a$, $\forall n \in \N \exists m \geq n: x_m \in U$.

    Such an $a$ exists because if $\forall a \in X$ there exists an neighborhood $U_a$ and a number $N_a$ such that
    \begin{align*}
      n \geq N_a \implies x_n \notin U_a
    \end{align*}
    then by compactness we could cover $X$ with finitely many $U_a$ and take the maximum of the $N_a$. What this would give us is that $x_n \notin X$ for $n \geq \max \{N_{a_1}, N_{a_2}, \ldots, N_{a_m}\}$, which does not make sense.

    By 1AA, let $\mathcal{U} = \{U_1, \ldots\}$ be a countable neighborhood basis of $a$.
    Just like in the previous proof we inductivley chose $n_1 \leq n_2 \leq \ldots \leq n_l \leq \ldots$ such that
    \begin{align*}
      x_{n_l} \in U_1 \cap \ldots \cap U_l
    \end{align*}
    which means $\lim_{l \to \infty} x_{n_l} = a$.

  \item  See Analysis II
\end{itemize}
\end{proof}


\begin{ex}[Counterexamples]
  The space $[0,1]^{[0,1]}$ is compact, but not sequentially compact.

  The \textbf{long line} is 1AA, sequentially copmact, but not compact.
\end{ex}

To better understand why we need the 2AA, we will quickly cover manifolds.

\subsection{Manifolds}
\begin{dfn}[]
A subset $M \subseteq \R^{n}$ is called a $d$-dimensional \textbf{smooth submanifold} of $\R^{n}$ if for all $p \in M$ there exist open sets $U_p,V_p \subseteq \R^{n}$ and a diffeomorphism $\phi_p: U_p \to  V_p$ with
\begin{align*}
  \phi_p(U_p \cap M) = \{y \in V_p \big\vert y_i = 0, \forall i > d\} = V_p \cap (\R^{d} \times 0)
\end{align*}
\end{dfn}
Another analogous definition is that of a \textbf{topological submanifold}, where we replace smoothness with continuity.

\begin{ex}[]
  We say in Analysis II that if $F: \R^{n} \to  \R^{m}$ is smooth and has a regular value $v \in \R^{m}$ (i.e. $\text{rank} DF = \min\{n,m\}$, then $F^{-1}(v)$ is a $(n-m)$-dimensional submanifold (if $n \geq m$).

  From this, we see that the torus can be written as the preimage of hte smooth function
  \begin{align*}
    F(x,y,z) = (x^{2} + y^{2} + z^{2} + R^{2} - r^{2})^{2} - 4R^{2}(x^{2} + y^{2})
  \end{align*}
\end{ex}



\begin{dfn}[]
Let $X$ be a topological space.
We say that $X$ is a $d$-dimensional \textbf{topological manifold}, if 
\begin{itemize}
  \item $\forall  p \in M$ there exists a $U \subseteq X$ open with $p \in U$ and $U \iso \R^{4}$
  \item $X$ is Hausdorff
  \item $X$ satisfies the 2AA
\end{itemize}
\end{dfn}
But why do we want the two extra requirements? 
The \textbf{Embedding theorem} gives us an answer:
The defintions we just saw are in a certain sense equivalent:
\begin{thm}[Embedding theorem]
  \phantom{a}
  \begin{enumerate}
    \item All topological submanifolds of $\R^{n}$ are topological manifolds.
    \item If $X$ is a topological manifold, then there exists an $n \in \N$ and a topological submanifold $M \subseteq \R^{n}$ such that $X \iso M$.
  \end{enumerate}
\end{thm}
\begin{proof}
  The first one trivial: Since subspaces of $\R^{n}$ are ausdorff and fulfill the 2AA.

  And if $p \in M$, then there exists $U_p,V_p \subseteq \R^{n}$ open and a homeomorphism $\phi_p:U_p \to V_p$.
  What might happen is that the $U_p$ can intersect $M$ at multiple points and so we need to trim $U_p$.

  Chose $\epsilon > 0$ such that $B_{\epsilon}(\phi_p(p)) \subseteq V_p$. Then
  \begin{align*}
    U := \phi_p^{-1}(B_{\epsilon}(\phi_p(p))) \cap M \subseteq M
  \end{align*}
  is open and isomorhpic to $\R^{d}$.

  
  Showing (b) is more difficult and is not done in the lecture. See the corresponding section in Munkres for the proof.
\end{proof}


\subsection*{Classification of $d$-dimensional compact path connected manifolds}
\begin{itemize}
  \item[$d=1$] All are homemorphic to $S_1$
  \item[$d=2$] All are homeomorphic to exactly one of the following surfaces
    \begin{align*}
      \Sigma_0 = \IS^{2}, \quad \Sigma_1 = \IS^{1} \times \IS^{1} = \mathbb{T}, \quad \ldots \Sigma_n = \text{ genus $n$ Torus}, \ldots
    \end{align*}
    also called the orientable surfaces of genus $n \in \N$,
    and the non-orientable surfaces
    \begin{align*}
      \Sigma_1^{\text{non-or}} = \R\IP^{2}, \Sigma_2^{\text{non-or}} = \text{Klein Bottle}, \ldots,\Sigma_k^{\text{non-or}},\ldots
    \end{align*}
\end{itemize}
An important lemma to prove the classification theorem is to show that these surfaces are all distinct.
\begin{lem}[]
Let $n,m \in \N$. If $\Sigma_n \sim \Sigma_m$, then $n=m$.
\end{lem}
The proof can be done using the fundamental group.
