\section{The Galois Correspondence}

One might ask if the inverse of Theorem \ref{thm:3-14} is true, that is: 
If $E/k$ is a normal extension for a polynomial $f \in k[X]$ and $\Gal(E/k)$ is resolvable, does that mean that $f$ is solvable by radicals?

More generally one might ask if there is a correspondence between subgroups of $\Gal(E/k)$ and sandwiched fields $k \subseteq B \subseteq E$.

It turns out that such a correspondence exists if we impose the property that $f$ be separable.
We wish to better understand this correspondence in this chapter.

Looking at the definition of the galois group of an extension $E/k$, it consists of automorphisms that keep the field $k$ fixed.
But what can happen is that the Galois group fixes more points than just $k$ and we want to find out when that is the case.

\begin{dfn}[]
  Let $E$ be a field and $H \subseteq \Aut E$ a subset. The set
  \begin{align*}
    E^{h} := \{a \in E \big\vert \sigma(a) = a \forall \sigma \in H\}
  \end{align*}
  is a subfield of $E$ called the \textbf{fixing field} of $H$.
\end{dfn}
Note that the map $H \mapsto E^{H}$ is contravariant with respect to inclusion
\begin{align*}
  H_1 \subseteq H_2 \implies E^{H_2} \subseteq E^{H_1}
\end{align*}

If $H$ is the galois group of a field extension $E/k$, then trivially $k \subseteq E^{\Gal(E/k)}$.

\begin{ex}[]
  Take for example $k = \F_p(t), f(X) = X^{p}-t$ and $E$ a splitting field of $f$.
  From the $X^{p}-c$ Lemma, we know that $\Gal(E/k) = \{e\}$, which shows $k \subsetneq E^{\Gal(E/k)} = E$.
\end{ex}

If $H < \Aut E$ is a finite subgroup, we can find out the order of the extension $E/E^{H}$.


In MMP-II, we saw that we can understand a group by studying its character table, where the characters are group homomorphisms of a group $G$ into the circle group $\IS^{1}$. 
Here we provide a more generalized definition
\begin{dfn}[]
  A \textbf{character} of a group $G$ in a field $E$ is a group homomorphism $\chi: G \to  E^{\times}$, into the multiplicative group of $E$.

  We denote the set of characters with $\Hom_{\Grp}(G,E^{\times})$.
  And we write
  \begin{align*}
    F(G,E) = \{\phi: G \to E\}
  \end{align*}
  for the $E$-vector space of $E$-valued functions on $G$.
\end{dfn}


Also from MMP-II, we know that the characters in $\Hom_{\Grp}(G,\IS^{1})$ fulfill the orthogonality relation.
For arbitrary fields $E$, we can get a weaker version:

\begin{prop}[Dedekind]\label{prop:dedekind}
  $\Hom_{\Grp}(G,E^{\times}) \subseteq F(G,E)$ is linearly independent.
\end{prop}
\begin{proof}
  If assume the opposite, then let $n \geq 2$ be the minimal number such that there exists characters $\chi_1, \ldots, \chi_n$ that are linarly dependend in $F(G,E)$, so
  \begin{align*}
    \exists c_1, \ldots, c_n \in E \setminus \{0\} \text{ with } c_1 \chi_1(x) + \ldots + c_n \chi_n(x) = 0 \quad \forall x \in G
  \end{align*}
  Since $\chi_1 \neq \chi_2$, there exists a $y \in G$ with $\chi_1(y) \neq \chi_2(y)$.
  By evaluating the above expressionat $x \cdot y$, we get
  \begin{align*}
    c_1 \chi_1(x) \chi_1(y) + \ldots + c_n \chi_n(x) \chi_n(y) = 0 \quad \forall  x \in G
  \end{align*}
  and after dividing by $\chi_n(y)$ and subtracting the original equation, we get
  \begin{align*}
    c_1
  \end{align*}
\end{proof}
\begin{center}
Missing 45 mins
\end{center}
